### 2018-07-24 README.Rmd
Add infer hex

# Infer

@@

<!--figs/infer.svg-->
<!--http://www.r-pkg.org/badges/version/infer-->
<!--figs/master.svg-->
<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

```{r diagram, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::include_graphics("https://raw.githubusercontent.com/andrewpbray/infer/master/figs/ht-diagram.png")
```

@@

```{r}
install.packages("remotes")
remotes::install_github("andrewpbray/infer")
```

@@

```{r}
install.packages("remotes")
remotes::install_github("andrewpbray/infer", ref = "develop")
```

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.

>>>>

# infer R Package <img src="https://github.com/tidymodels/infer/blob/develop/figs/infer_gnome.png?raw=true" align="right" width=125 />

@@

<!--figs/infer.svg-->
<!--http://www.r-pkg.org/badges/version/infer-->
<!--figs/master.svg-->
<!--https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg-->

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)

@@

```{r diagram, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
```

@@

```{r}
install.packages("remotes")
remotes::install_github("tidymodels/infer")
```

@@

```{r}
install.packages("remotes")
remotes::install_github("tidymodels/infer", ref = "develop")
```

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/tidymodels/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.
